Type cones of $\b{g}$-vector fans

### 2019-02-04 thirdPaper/draft/typeConeAssociahedra.tex
Completed first draft of Section 3 and added references.

%%%%
\subsection{Statement of the theorem}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
\[
 F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
\]
\begin{proposition}[]\pg{Add references to BMR and KR}
 The functor~$F$ induces an equivalence of~$\field$-linear categories
 \[
  F:\cat/(\susp T) \xrightarrow{} \MOD \Lambda,
 \]
 where~$(\susp T)$ is the ideal of morphisms factoring through an object of~$\add(\susp T)$ and~$\MOD \Lambda$ is the category of finite-dimensional right~$\Lambda$-modules.  This equivalence induces further equivalences between~$\add(T)$ and the category of projective modules, and between~$\add(\susp^2 T)$ and that of injective modules.
\end{proposition}

@@

\begin{proposition}[]\pg{Cite Palu}
 For any pair of objects~$X$ and~$Y$ in~$\cat$, there is an isomorphism of bifunctors
 \[
  (\susp T)\cat(X, \susp Y) \xrightarrow{\cong} \cat(Y, \susp X)/(\susp T),
 \]
 where~$(\susp T)\cat(X, \susp Y)$ is the space of morphisms from~$X$ to~$Y$ factoring through~$(\susp T)$.
\end{proposition}

\begin{remark}
 Although the field~$\field$ is assumed to be algebraically closed in~\cite{} \pg{Cite Palu}, this assumption is not needed in the proof, and the result is valid over any field.
\end{remark}

@@

\begin{definition}
 \begin{enumerate}
  \item Let~$\Ksp(\cat)$ be the \defn{split Grothendieck group} of~$\cat$, that is, the free abelian group generated by symbols~$[X]$, where~$[X]$ denotes the isomorphism class of~$X$ in~$\cat$, modulo the following relations: for any objects~$Y$ and~$Z$, we let~$[Y\oplus Z] = [Y] + [Z]$.

@@

\end{definition}
In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.  The choice of the notation for~$\Kg(\cat)$ is motivated by the next section \pg{Add ref}, where we study relations between~$\b g$-vectors.

@@

 Now,~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is a sub-module of~$\cat(\susp^{-1} X, \susp X)$.  Therefore, if~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is non-zero, then it contains the one-dimensional socle of~$\cat(\susp^{-1} X, \susp X)$, and thus contains~$h$.   
 By \cite{} \pg{cite Palu},
 \[
  (\susp T)\cat(\susp^{-1} X, \susp X) \cong D\cat(X, X)/(\susp T). 
 \]
The identity morphism of~$X$ is not in~$(\susp T)$, since~$X$ is not in~$\add(\susp T)$.  Thus the right-hand side is non-zero, and so neither is the left-hand side.  By the above, this implies that~$h\in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
\end{proof}

@@

@@

\begin{proposition}
 Assume that the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
\end{proposition}
\begin{proof}

\end{proof}

\pg{TO DO}

%%%%
\subsection{Application to~$\b g$-vectors}

We recall the following results and definition from \cite{} \pg{cite DK and Palu}.

@@

The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{} \pg{ref}.  The link is given by the following result.

\begin{proposition}[]\pg{cite Palu}
 Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
 Then
 \[
  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
 \]
 if and only if~$h\in (\susp T)$.
\end{proposition}

>>>>

%%%%
\subsection{Statement of the theorem}
We need to introduce some notations before stating the main result of this section.  Let~$\Lambda:= \End{\cat}(T)$, and let~$F$ be the functor
\[
 F=\cat(T,-):\cat \xrightarrow{} \MOD \Lambda.
\]
\begin{proposition}[\cite{BuanMarshReiten, KellerReiten}]
 The functor~$F$ induces an equivalence of~$\field$-linear categories
 \[
  F:\cat/(\susp T) \xrightarrow{} \MOD \Lambda,
 \]
 where~$(\susp T)$ is the ideal of morphisms factoring through an object of~$\add(\susp T)$ and~$\MOD \Lambda$ is the category of finite-dimensional right~$\Lambda$-modules.  This equivalence induces further equivalences between~$\add(T)$ and the category of projective modules, and between~$\add(\susp^2 T)$ and that of injective modules.
\end{proposition}

@@

\begin{proposition}[\cite{Palu}]
 For any pair of objects~$X$ and~$Y$ in~$\cat$, there is an isomorphism of bifunctors
 \[
  (\susp T)\cat(X, \susp Y) \xrightarrow{\cong} \cat(Y, \susp X)/(\susp T),
 \]
 where~$(\susp T)\cat(X, \susp Y)$ is the space of morphisms from~$X$ to~$Y$ factoring through~$(\susp T)$.
\end{proposition}

\begin{remark}
 Although the field~$\field$ is assumed to be algebraically closed in~\cite{Palu}, this assumption is not needed in the proof, and the result is valid over any field.
\end{remark}

@@

\begin{definition}\label{defi::grothendieck-group}
 \begin{enumerate}
  \item Let~$\Ksp(\cat)$ be the \defn{split Grothendieck group} of~$\cat$, that is, the free abelian group generated by symbols~$[X]$, where~$[X]$ denotes the isomorphism class of~$X$ in~$\cat$, modulo the following relations: for any objects~$Y$ and~$Z$, we let~$[Y\oplus Z] = [Y] + [Z]$.

@@

\end{definition}
In particular,~$\Ksp(\cat)$ is isomorphic to a free abelian group over the set~$\ind(\cat)$.  The choice of the notation for~$\Kg(\cat)$ is motivated by Section~\ref{sect::applications-g-vectors}, where we study relations between~$\b g$-vectors.

@@

 Now,~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is a sub-module of~$\cat(\susp^{-1} X, \susp X)$.  Therefore, if~$(\susp T)\cat(\susp^{-1} X, \susp X)$ is non-zero, then it contains the one-dimensional socle of~$\cat(\susp^{-1} X, \susp X)$, and thus contains~$h$.   
 By \cite{Palu},
 \[
  (\susp T)\cat(\susp^{-1} X, \susp X) \cong D\cat(X, X)/(\susp T). 
 \]
The identity morphism of~$X$ is not in~$(\susp T)$, since~$X$ is not in~$\add(\susp T)$.  Thus the right-hand side is non-zero, and so neither is the left-hand side.  By the above, this implies that~$h\in (\susp T)\cat(\susp^{-1} X, \susp X)$, which finishes the proof.
\end{proof}

@@

\begin{corollary}
 If~$\ind(\cat)$ is finite, then the set~\[\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \} \cup \{[\susp T_i] \ | \ i=1, \ldots, n\}\] is a basis of~$\Ksp(\cat)$.
\end{corollary}
\begin{proof}
 By Proposition~\ref{prop::free-set}, the set is free.  It suffices to prove that it generates~$\Ksp(\cat)$.  Let~$x\in \Ksp(\cat)$.  Consider
 \[
  z = x - \sum_{A\in \ind{\cat}} \frac{\langle x, A \rangle}{\langle \ell_A, A\rangle} \ell_A.
 \]
 Then for any~$B\in \ind(\cat)$, we have that~$\langle z, [B] \rangle = 0$.  By Lemma~\ref{lemm::test-susp-T}, this implies that~$z\in \Ksp(\add(\susp T))$, and finishes the proof.
\end{proof}

@@

\begin{proposition}
 Assume that the set~$\{[\ell_A] \ | \ A\in \ind(\cat) \setminus \add(\susp T) \}$ is a basis of the kernel of~$\b g$. Then~$\ind(\cat)$ is finite.
\end{proposition}
\begin{proof}
 Let~$x\in \ker \b g$, and write~$x = \sum_{[A]\in \ind(\cat)} \lambda_A[A]$, where the sum has finite support.  For any~$B$ not in the support of the sum, we have that~$\langle x, [B] \rangle = 0$.

 Now,~$[T]+[\susp T]$ is in the kernel of~$\b g$, but~$\langle [T] + [\susp T], [B] \rangle = \langle [T], [B] \rangle = 0$ if and only if~$B\in \add(\susp T)$.  Thus~$\ind(\cat)$ has to be finite.
\end{proof}

%%%%
\subsection{Application to~$\b g$-vectors}\label{sect::applications-g-vectors}

We recall the following results and definition from \cite{DehyKeller,Palu}.

@@

The notion of index is very close to the definition of the map~$\b g:\Ksp(\cat)\to \Kg(\cat)$ of Definition~\ref{defi::grothendieck-group}.  The link is given by the following result.

\begin{proposition}[\cite{Palu}]
 Let~$X\xrightarrow{} Y \xrightarrow{} Z \xrightarrow{h} \susp X$ be a triangle.
 Then
 \[
  \ind_T(X) + \ind_T(Z) - \ind_T(Y) = 0
 \]
 if and only if~$h\in (\susp T)$.
\end{proposition}
